\section*{Corrections}
%
A record of amendments made to the thesis in the wake of the viva.
%
Non-trivial (non-typographic/notational) errors have been coloured \corr{blue} for salience.
%
\begin{itemize}
    %
    \item All typographic and notational errors highlighted by the examiners have been amended.
    %
    \item (pp.6,8) Footnotes with references to the publications underpinning Chapters 3 and 5 have
        been added to the chapter summaries at the end of the Introduction.
    %    
    \item (p.19) CelebA example provided in viva has been added to clarify the failure mode of DANN
        and related methods arising due to correlation between the target and subgroup (domain)
        attribute.
    %
    \item (p.51) Fig. 3.1 has been relocated to a point adjacent to the first in-text reference to
        it. 
        %
        The caption has been greatly expanded, now addressing the involvement (or lack thereof) of
        null-sampling during training, this being a major point of confusion raised by the external
        examiner during the viva.
    %
    \item (p.53) Statement on the shortcomings of relying on a binary mechanism when the underlying
        subgroup attribute is continuous has been clarified/reworked -- the reference to
        non-linearity has been removed due to its being misleading.
    %
    \item (p.54) A reference to the appendix providing (preliminary) empirical evidence of the
        hypothesis of increased OOD-robustness has been included here (together with some
        rephrasing).
    %
    \item (p.57) Added conjecture on the sub-ERM performance of the Ln2L baseline, namely it being
        a result of the method's adversarial mutual-information-minimisation driving the encoder
        towards a digit-invariant solution on account of the strong spurious correlation.
    %
    \item (p.61) Added explanation about the sub-baseline accuracy of our models being a natural
        consequence of the accuracy-fairness trade-off.
    %
    \item (p.70) Personal contributions to Chapter 3 have been elaborated on.
    %
    \item (p.84) The use of the mean of the projected representations as the query in the bag-wise
        aggregation function has been clarified in the main text.
        %
        A note on the instance-wise and bag-wise objectives having theoretically -- but not
        empirically-equivalent solutions (as adverted to by the external examiner) -- has been
        added.
    %
    \item (pp.91,92) The conclusion to the main text in Chapter 3 has been augmented with details
        of ongoing work, work that includes efforts to shore up the paucity/syntheticity of the
        tested-on datasets as well as conduct sensitivity analyses \wrt{} bag-balancing.
    %
    \item (p.122) The caption of Fig. 5.1 has been substantially expanded to now contain summaries
        of the two calipers and explanation of the red crosses (denoting exclusion from the
        candidate pool) added over the course of the pipeline. Readers in search of more details
        regarding the calipers and their motivation are referred to the RealPatch paper introducing
        them.
    %
    \item (p.151) Added paragraph to limitations section of Discussion noting the
        syntheticity/paucity of the datasets experimented with in Chapters 3 and 4.
    %
\end{itemize}
