% ********************************************************************************
\section{ Semi-supervised Learning }\label{sec:semisl}
% ********************************************************************************
Given that this thesis references semi-supervised learning (SemiSL)
%
\footnote{ Since self-supervised learning also features prominently in this thesis (primarily in
Chapter 5) we must depart from the typical initialism, SSL, so as to be able to differentiate the
two learning paradigms. }
%
in its title, it is only appropriate that a part of this background section be devoted to the
topic.
%
However, we note that the methods introduced in this thesis are not tailored for the typical SemiSL
regime wherein one hopes to draw upon a large corpus of unlabelled data to shore up the paucity of
annotated data available for direct supervision, with the assumption being that the unlabelled and
labelled data are drawn from the same distribution.
%
Rather, the theme across the constituent papers is how one can use unlabelled data to redress
representational bias and failures in out-of-distribution generalisation. 
%
The problem setups considered thus more closely align with those found in DG and DA; we have
afforded more attention to those topics for this reason.

We would refer the reader to \cite{chapelle2009semi} for excellent (in both clarity and depth)
exposition of theory underpinning SemiSL learning and methods in the pre-deep-learning era, a book
we will reference extensively throughout this brief overview of the topic.
%
For a for comprehensive and current survey of SemiSL methods in the post-deep-learning, on the
other hand, we refer the reader to \cite{yang2022survey}.

%
% References to consider: \cite{chapelle2009semi, scholkopf2021toward, lienen2021credal,
% sohn2020fixmatch, tarvainen2017mean, blum1998combining, gong2021alphamatch}
%

% --------------------------------------------------------------------------------
\subsection{Cluster assumption.}\label{ssec:cluster-assumption}
% --------------------------------------------------------------------------------
%
% --------------------------------------------------------------------------------
\subsection{Low-density-separation assumption.}\label{ssec:lds-assumption}
% --------------------------------------------------------------------------------
%
% --------------------------------------------------------------------------------
\subsection{Smoothness assumption.}\label{ssec:smoothness-assumption}
% --------------------------------------------------------------------------------
% --------------------------------------------------------------------------------
\subsection{
  Causal connections: when should/shouldn't SemiSL work?
}\label{ssec:semisl-causality}

Following \cite{scholkopf2021toward}, start by supposing that our prediction task follows the
causal factorisation \( X \to Y\), i.e. it is a causal, rather than an anticausal, one.
%
As discussed before, the ICM principle states that modules in a joint distribution's causal
decomposition do not inform or influence one another, i.e. \(\gI(X, Y) = 0 \); this implies that in
the when \(X\) is the causal parent to \(Y\), as in the supposed case, a better estimate of
\(P(X)\) does not yield a better estimate of \(P(Y|X)\) and it is the former that SemiSL
compasses to learn using unlabelled data.
%
However, that is not to say that SemiSL as in its totality is misguided, it merely requires the
right condition to be met, that condition (which applies to a wide-range of real-world problems)
being the contrary factorisation, \(Y \to X \), which is to say that that the task under
consideration is anticausal.
%
In this case, \(X\) can contain information about the labelling mechanism, as \(X\) is now the
effect, and \(Y\) is now the cause opening up the possibility of exploiting dependencies in the
marginal distribution to better estimate the conditional distribution; in
\cite{scholkopf2012causal} the authors test corroborate this hypothesis.
%
While perhaps often overlooked, this requirement, in fact, well-aligned with the motivating
arguments for SemiSL that we discussed at the beginning of this section.
%
The \emph{cluster assumption} predicates that points belonging to the same cluster in \(P(X)\)
abide by the same labelling mechanism; 
%
the \emph{low-density} assumption predicates that the region in which \(P(Y|X)\) is maximally
entropic (defining the decision boundary) should have low \(P(X)\), or, by invocation of Bayes'
Theorem, low \( \frac{ P(X|Y)P(Y) }{ P(Y|X) } \); 
%
the \emph{smoothness assumption} predicates that if two inputs in a high-density region are close,
then their respective images (under the model) also should be -- this can be viewed as imposing a
kind of \(K\)-Lipschitz or \(\epsilon\)-isometric constraint on our function class;
%
notice that in all three of these cases the causal factorisation is implied to be \(Y \to X \).
%
The celebrated co-training theorem \citep{blum1998combining} similarly respects this precondition
of anticausality in assuming that the co-trained predictors are conditionally independent given the
label, as one have if the label were the cause (the causal parent in the bivariate causal graph).
%
Points from \cite{castro2020causality} to integrate into the above discussion:
\begin{itemize}
        \item One of the notorious challenges in medical image analysis is that of scarcity of
          labelled data, owing to the high costs (lab tests) and expertise required  for
          annotation.
        \item In many cases, establishing the causal direction between inputs and prediction
          targets is non-trivial, particularly if crucial metadata is missing.
        \item Strong requirements need to be bet for SemiSL to be fruitful, namely, the
          distribution of inputs needs to carry information relevant to the prediction task.
          %
          This idea is typically articulated in terms of specific assumptions about the data:
          similar inputs are likely to have similar labels (smoothness assumption) and will
          naturally group into clusters with high density in the input features space (cluster
          assumption). Lower density regions in that space in-between clusters are assumed to be
          ideal candidates for fitting decision boundaries.
          %
          In this context, considering large amounts of unlabelled data together with scarce
          labelled data may reveal such low density regions.
          %
          Note how this idea insinuates and interplay between the distribution of inputs, \( P(X)
          \), and the conditional distribution \( P(Y|X) \). 
          %
          Recall that by the ICM principle, if the prediction task is causal, then the marginal
          distribution \( P(X) \) is uninformative \wrt{} \( P(Y|X) \) and SSL is theoretically
          futile.
          %
          Since typical semantic segmentation tasks are causal, there is likely very little hope
          that semantic segmentation can fundamentally benefit from unlabelled data.
          %
          A model trained on image-derived annotations will attempt to predict some pre-imaging
          ground-truth. 
          It is plausible that seeing more raw images without corresponding anatomical information
          provides no new insight about the labelling mechanism.
          %
          Conversely, if \( Y \to X \), as for skin lesions, then these distributions may be
          dependent and semi-supervision has a chance of success.
          %
          That is not to say that SSL is completely  useless for causal tasks; there can be
          practical algorithmic benefits.
          %
          Namely, under certain conditions, unlabelled data can be shown to have a regularising
          effect and may reduce the amount of labelled data required to achieve a given performance
          level \citep{chapelle2009semi}
          %
          A recent empirical study \citep{oliver2018realistic} reported that properly-tuned
          supervised models, either pretrained on trained on only the task-relevant data, are often
          competitive with or outperform their semi-supervised counterparts. Also shown here was
          the potential for SemiSL to harm performance under label shift.
          %
          ``
          We find that the performance of simple baselines which do not use unlabelled data is
          often under-reported, SSL methods differ in sensitivity to the amount of labelled and
          unlabelled data, and performance can degrade substantially when the unlabelled dataset
          contains out-of-distribution examples
          %
          \begin{itemize}
            \item When given equal budget for tuning hyperparameters, the gap in performance
              between using SSL and using only labelled data is smaller than typically reported.
              %
            \item A large classifier with carefully chosen regularization trained on a small
              labeled dataset with no unlabelled data can reach very good accuracy.
              %
            \item This demonstrates the importance of evaluating different SSL algorithms on the
              same underlying model.
              %
            \item In some settings, pre-training a classifier on a different labelled dataset and
              then retraining on only labelled data from the dataset of interest can outperform all
              SSL algorithms we studied.
              %
            \item Performance of SSL techniques can degrade drastically when the unlabelled data
              con • Different approaches exhibit substantially different levels of sensitivity to
              the amount of labelled and unlabelled data.
          ''
\end{itemize}

% % --------------------------------------------------------------------------------
% \subsection{A (brief) taxonomy of semi-supervised methods}
% % --------------------------------------------------------------------------------

